Structural Divergence Analysis

### 2017-03-26 analysis-structure.Rmd
paper actualizado

```{r set-my-colors}
# set my colors
myColors = c("blue", "darkgreen", "darkgreen", "red", "red") 
names(myColors) <- c("exp", "mut", "no-sel", "strong", "strong-sel")
```

@@

```{r-mean-se-z.RSD-vs-site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}
# comparison of z.RSD profiles with functional sites
## prepare dat
dat = siteComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("strong" = "strong-sel"))
dat$dataset = revalue(dat$dataset, c("mut" = "no-sel"))

@@

p.facet %+% subset(d, dataset == "exp") 
p.facet %+% subset(d, dataset == "no-sel")
p.facet %+% subset(d, dataset == "strong-sel") 
p.facet

@@

# calculate correlations berween profiles
d.exp = subset(d, dataset == "exp")
d.mut = subset(d, dataset == "no-sel")
d.strong = subset(d, dataset == "strong-sel")

@@

# calculate de mean.p.accept of simulated data
mean.p.accept.no.sel = c()
mean.p.accept.strong.sel = c()

if (data.dir == "OUT/out_subset_CM_ANM") {
  mut.site.no.sel = mut.site.no.sel - n.sites
  mut.site.strong.sel = mut.site.strong.sel - n.sites
  CN.CM = sim.data.no.sel$CN
  CN = c()

@@

```
```{r structure-profiles-comparison}

@@

knitr::kable(cor.df, digits = 2, caption = "Correlation between sequence profiles")
```

>>>>

```{r set-my-colors}
# set my colors
myColors = c("blue", "darkgreen", "darkgreen", "red", "red") 
names(myColors) <- c("exp", "mut", "no-selection", "strong", "selection")
```

@@

```{r-mean-se-z.RSD-vs-site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}
# comparison of z.RSD profiles with functional sites
## prepare dat
dat = siteComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("strong" = "selection"))
dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

@@

p.facet %+% subset(d, dataset == "exp") 
p.facet %+% subset(d, dataset == "no-selection")
p.facet %+% subset(d, dataset == "selection") 
p.facet

@@

# calculate correlations berween profiles
d.exp = subset(d, dataset == "exp")
d.mut = subset(d, dataset == "no-selection")
d.strong = subset(d, dataset == "selection")

@@

# calculate mean.p.accept of simulated data
mean.p.accept.no.sel = c()
mean.p.accept.strong.sel = c()

# correct indexes
if (data.dir == "OUT/out_subset_CM_ANM") {
  mut.site.no.sel = mut.site.no.sel - n.sites
  mut.site.strong.sel = mut.site.strong.sel - n.sites
  CN.CM = sim.data.no.sel$CN
  CN = c()

@@

```
```{r structure-profiles-CN-comparison}

@@

knitr::kable(cor.df, digits = 2, caption = "Correlation structure - sequence")
```
